### 2017-04-30 paper/jfp-submission/evaluation.tex
get rid of interaction trace language, seems to bother RJ

We answer the last question on a subset of the \ucsdbench dataset.
%
For each ill-typed program in a student's interaction trace, we identify
the student's \emph{fix} by searching for the first type-correct program
that follows it in the trace.
%
We then use an expression-level \emph{diff}~\cite{Lempsink2009-xf} to
determine which sub-expressions changed between the ill-typed program
and the student's fix, and treat those expressions as the source of the
type error.

>>>>

We answer the last question on a subset of the \ucsdbench dataset.
%
% For each ill-typed program in a student's interaction trace, we identify
% the student's \emph{fix} by searching for the first type-correct program
% that follows it in the trace.
For each ill-typed program compiled by a student, we identify the student's
\emph{fix} by searching for the first type-correct program that the student
subsequently compiled.
%
We then use an expression-level \emph{diff}~\cite{Lempsink2009-xf} to
determine which sub-expressions changed between the ill-typed program
and the student's fix, and treat those expressions as the source of the
type error.
